Longitudinal Data Cleaning

### 2021-02-26 report_alt.Rmd
Compare the threshold of weight.

---
title: "Longitudinal Data Cleaning"
subtitle: "A Case of The NLSY79 Data"
author: "Dewi Lestari Amaliah"
date: "24/02/2021"
output: 
  bookdown::pdf_document2:
    toc : false
bibliography: references.bib
---

@@

This paper aims to demonstrate the steps of IDA, which is tidying, cleaning, and documenting the data. We used the longitudinal wages data of Americans from the National Longitudinal Survey of Youth 1979 or is known as the NLSY79.

@@

@@

## Getting and Tyding the Data

>>>>

---
title: "Longitudinal Data Cleaning"
subtitle: "A Case of The NLSY79 Data"
author: "Dewi Lestari Amaliah, Dianne Cook, Emi Tanaka, Nicholas Tierney, Kate Hyde"
date: "24/02/2021"
output: 
  bookdown::pdf_document2:
    toc : false
bibliography: references.bib
---

@@

This paper aims to demonstrate the steps of IDA, which is tidying, cleaning, and documenting the data. We used the longitudinal data of Americans from the National Longitudinal Survey of Youth 1979 or is known as the NLSY79. Particularly, we are interested in doing the IDA to the wages and several demographic variables of the cohort whose highest grade are up to 12th grade and the high school dropouts.

@@

The NLSY79  is a longitudinal survey held by the U.S Bureau of Labor Statistics that follows the lives of American Youth a sample of American youth born between 1957-64. The cohort originally included 12,686 respondents ages 14-22 when first interviewed in 1979. There were three race interviewed in the survey, which are Black, Hispanic, and non-Black/non-Hispanic. In 1984 interview, 1,079 members of the military sample were no longer eligible for interview; 201 respondents randomly selected from the military sample remained in the survey. Following the 1990 interview, none of the 1,643 members of the economically disadvantaged, non-Black/non-Hispanic sample were eligible for interview. Hence, 9,964 respondents remain in the eligible samples. The surveys were conducted annually from 1979 to 1994 and biennially thereafter. Data are now available from Round 1 (1979 survey year) to Round 28 (2018 survey year).

The NLSY79 covers several topics including Education, Training & Achievement Scores; Employment; Household, Geography & Contextual Variables; Family Background; Dating, Marriage & Cohabitation, Sexual Activity, Pregnancy & Fertility; Children; Income, Assets & Program Participation; Health; Attitudes & Expectations; and Crime and Substance Use.

@@

## Getting and Tidyng the Data
